Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-08 paper/paper.tex
minor word changes to abstract.

\begin{abstract}
    When a small pattern graph does not occur inside a larger target graph, we can ask how to find
    ``as much of the pattern as possible'' inside the target graph. In general, this is maximum
    common subgraph problem, which is much more computationally challenging in practice than
    subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
    vertices from the pattern can be found in the target. This allows us to develop slightly
    weakened forms of certain invariants from subgraph isomorphism, retaining most of their
    effectiveness. For small values of $k$, we can solve this problem on most of the standard problem
    instances used to benchmark subgraph isomorphism algorithms, despite these instances being much
    too large for current maximum common subgraph algorithms to handle.
\end{abstract}

>>>>

\begin{abstract}
    When a small pattern graph does not occur inside a larger target graph, we can ask how to find
    ``as much of the pattern as possible'' inside the target graph. In general, this is known as
    the maximum common subgraph problem, which is much more computationally challenging in practice
    than subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
    vertices from the pattern can be found in the target. This allows for the development of
    slightly weakened forms of certain invariants from subgraph isomorphism, while retaining most
    of their effectiveness. For small values of $k$, we solve this problem on most of the standard
    problem instances used to benchmark subgraph isomorphism algorithms, despite these instances
    being too large for current maximum common subgraph algorithms to handle.
\end{abstract}
